Our experimental setup consists of five parts (see Figure~\ref{fig:pipeline}) but the 
respective parts differ slightly depending on whether we test non-overlapping or overlapping 
communities. We use the LFR benchmark graph generator developed by Lancichinetti, 
Fortunato, and Radicchi~\cite{LFR08,LF09}, which outputs graphs where the community 
information of each node is known. From each community in the graph thus generated, 
we pick a fixed number of seed nodes per community and give these as input to our algorithm. 
Once the algorithm outputs the affinities of all non-seed nodes, we classify them into 
communities and finally compare the output with the ground truth using 
normalized mutual information (NMI) as a metric~\cite{DDDA05}. We implemented 
our algorithm in \CPP\ and Python and the code is available online.\footnote{At 
\texttt{https://github.com/somnath1077/CommunityDetection}}


\paragraph{LFR.}
We briefly describe the major parameters that the user has to supply 
for generating benchmark graphs in the LFR suite. The node degrees and the 
community sizes are distributed according to power law, with different exponents. 
An important parameter is the \emph{mixing parameter~$\mu$} which is the fraction of neighbors 
of a node that do not belong to any community that the node belongs to, averaged over all nodes.
The other parameters include maximum node degree, average node degree, 
minimum and maximum community sizes. For generating networks with overlapping communities, 
one can specify what fraction of nodes are present in multiple communities.


In what follows, we describe tests for non-overlapping and overlapping communities separately, since 
there are several small differences in our setup for these two cases. 

\subsection{Non-overlapping communities}
The networks we test have either 1000 nodes or 5000 nodes. The average node degree
was set at 20 and the maximum node degree set at 50. The parameter controlling the 
distribution of node degrees was set at~2 and that for the community size distribution was 
set at~1. Moreover, we distinguished between big and small communities: small communities have 
10--50 nodes and large communities have 20--100 nodes. 
For each of the four combinations of network and community size, we generated graphs with the 
above parameters and with varying mixing parameters. For each of these graphs, we tested the 
community information output by our algorithm and compared it against the ground truth 
using the normalized mutual information as a metric. The plots in the next section 
show how the performance varies as the mixing parameter was changed. Each data point in 
these plots is the average over 100 iterations using the same parameters. 

Due to lack of space, the exact details of how we generate seed nodes, classify nodes into 
communities and iteratively improve the classification is relegated to the appendix. 

\subsection{Overlapping Communities.}
The LFR benchmark suite can generate networks with an overlapping community structure. 
In addition to the parameters mentioned for the non-overlapping case, there is an additional 
parameter that controls what fraction of nodes of the network are in multiple communities. 
As in the non-overlapping case, we generated graphs with 1000 and 5000 nodes with the average
node degree set at 20 and maximum node degree set at 50. We generated graphs with two types 
of community sizes: small communities with 10--50 nodes and large communities with 20--100 nodes.
Moreover, as in~\cite{LF09}, we chose two values for the mixing factor: $0.1$ and $0.3$ 
and we plot the quality of the community structure output by the algorithm 
(measured by the NMI) against the fraction of overlapping nodes in the network.

As in the non-overlapping case, the details of seed node generation, community classification 
and the iterative technique to improve the classification are dealt with in the appendix.


